%========================================================================
% Chapter 6: Conclusion and Future Work
%========================================================================
\chapter{Conclusion and Future Work}

The NepTube project successfully delivered a comprehensive, AI-powered video streaming platform that meets the needs of both creators and viewers. Key objectives such as secure authentication \cite{clerk2024docs}, seamless video uploads \cite{uploadthing2024docs}, personalized recommendations \cite{covington2016deep, koren2009matrix}, and interactive community features were achieved. The platform demonstrated robust performance, scalability \cite{wang2019webscale}, and user engagement, positioning NepTube as a modern solution in the online streaming domain.

\section{Limitations}

\begin{itemize}[leftmargin=2cm]
  \item Ad integration within the video player was not implemented in the current version.
  \item Some advanced analytics and monetization features are limited in scope.
  \item AI moderation, while effective, may occasionally miss nuanced content issues.
  \item Testing was primarily manual, lacking automated test coverage.
\end{itemize}

\section{Future Enhancements}

\begin{itemize}[leftmargin=2cm]
  \item Integrate ad content seamlessly within the video player to support monetization.
  \item Expand analytics and reporting tools for creators and admins.
  \item Enhance AI moderation with more sophisticated models \cite{risch2020toxic} and multilingual support.
  \item Implement automated testing frameworks for improved reliability.
  \item Introduce additional community features such as live streaming and advanced chat options.
  \item Optimize platform performance for larger user bases and global scalability.
\end{itemize}

In conclusion, NepTube lays a strong foundation for an innovative streaming platform. Addressing current limitations and pursuing future enhancements will further elevate its capabilities and impact in the digital media landscape \cite{elinext2025ai}.
